Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131-1231 at $z$=0.654

### 2016-07-04 WRITEUP/ms.tex
updated with DR's comments and also shortened discussion on the merger stage, etc

\title{Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1231 at $z$=0.654}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

%==============================================================================
%                                Front matters
%==============================================================================

\begin{abstract}
We \bco observations with the \pdbi.
evidence for differential lensing.
wet-merger, Dynamical lens modeling
the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
% Our results support the hypothesis.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}

In this paper, we explore the ISM properties of the quadruply imaged
quasar RXS J113151.62-123158 (hereafter RXJ1131) at
$z_\textrm{AGN}$\,$=$\,0.685, with an Einstein ring of size
1\farcs83 in radius. The foreground lensing
galaxy is an elliptical galaxy at $z_\textrm{L}$\,$=$\,0.295. The redshifts
are spectroscopically confirmed by \citet{Sluse03a}.
A black hole mass estimate of M$_{\rm BH}$\,$<$\,2\E{8}\Msun
is also reported based on X-ray observations \citep{Reis14a}.

This paper is structured as follows.
In \Sec{obs} and \Sec{HST}, we outline the details of the observations and data reduction process.
In \Sec{results}, we report the measurements of the CO lines and photometry from optical to radio wavelengths.
In \Sec{anal}, we represent our dynamical lens modeling on the \bco data and the physical properties inferred for  RXJ1131.
In \Sec{diss}, we discuss the results and implications of this study in the context of molecular gas evolution in mergers and massive galaxies.
Finally, we summarize the main results of this study and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = 69.32 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.29, and
$\Omega_{\Lambda}$ = 0.71 \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco} % DONE
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,230.5379938 GHz; $\nu_{\rm obs}$\,=\,139.4\,GHz)
toward the \gl galaxy RXJ1131-1231 at $z_{\rm QSO}$\,=\,0.658
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX001; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively. The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup providing
an effective bandwidth of 3.6 GHz and a spectral resolution of 10.0 MHz ($\sim$
21.5 \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The nearby quasars 1127$-$145 and 1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and 1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding $\lesssim$15\% calibration accuracy.

The \ncode{gildas} package was used to reduce and analyze the visibility data
which are then imaged and deconvolved using the CLEAN algorithm with ``natural"
weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
The final rms noise is $\sigma$\,=\,1.45\,mJy\,\kms
beam\pmOne over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
is created by averaging over all the 3.16\,GHz line-free channels. This
yields an rms noise of 0.082 mJy\,beam$^{-1}$. % see README.md in 04Sep15

\subsection{CARMA \cco} %DONE
Observations of the \cco rotational line in RXJ1131
($\nu_{\rm rest}$\,=\,345.7959899\,GHz; $\nu_{\rm rest}$\,=\,209.1\,GHz)
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions. The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks. This results in a total on-source time of 2.94 hours after flagging poor
visibility data.

% poor phase note
% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
% rms scatter over ~ 90 klambda
% max baseline of obs. is 145 m
%
% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710
%
Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$60\degr over $\sim$135\,m.
%BLAH... more like 50%
We thus conservatively estimate
a calibration accuracy of $\sim$45\% based on the flux scale uncertainties,
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat its line intensity with caution and ensure that any physical interpretation
of this system does not rely on this quantity.

The \ncode{miriad} package was used to calibrate the visibility data which are
then imaged and deconvolved using the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA\,=\,8\degr) for the lower sideband
image cube. The final rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$
over a channel width of 25\,MHz. An rms noise of
$\sigma$\,=\,0.83\,mJy\,beam\pmOne is reached by averaging over the
line-free channels.

\subsection{VLA (Archival)} %DONE
Our analysis also uses archival data of the 5\,GHz
radio continuum obtained with the
Very Large Array (VLA; Program ID: AW741; PI: Wucknitz).
Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C$-$band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz in each sideband.
The nearby radio quasar 1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration, 1331$-$305 was observed as the
primary flux calibrator, and 0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We use \ncode{aips} to calibrate the visibility data which
are then imaged and deconvolved using
the CLEAN algorithm using robust\,=\,0. This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0\farcs18) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

\section{HST astrometry} \label{sec:HST}
We obtained an {\it HST} image taken with the F555W filter ($V$-band)
using the ACS/Wide Field Camera from the
Hubble Legacy Archive\footnote{Based on observations
made with the NASA/ESA Hubble Space Telescope, and obtained from the Hubble
Legacy Archive, which is a collaboration between the Space Telescope Science
Institute (STScI/NASA), the Space Telescope European Coordinating Facility
(ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).}
with a goal to understand the origin of the emission detected
in our mm observations. The details of the observations can be found
in \citet[hereafter C06]{Claeskens06a}.
We adopt the VLA 5\,GHz map of
$\sim$0\farcs5 resolution as the
reference coordinate frame to align the optical ($V$-band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$^{\prime\prime}-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. This astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is guided by its
coordinates in the optical image, where its emission is clearly detected.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have an astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR, phase
instabiliy, and beam size.
\defcitealias{Claeskens06a}{C06}

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\subsection{\bco Emission} \label{sec:CO21} %DONE
We detected the \bco line emission toward the background galaxies
at $\gtrsim$27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
0.65370\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
is with respect to $z$=0.6537, which is approximately the line center
considering the asymmetry as a result of differential lensing.
A detailed discussion of this effect is presented in
\Sec{differential} and the magnification factors for various kinematic
components are listed in \Tab{model}.
 \label{fig:CO21spec}}
\end{figure}

% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct the zeroth moment map and the renzogram in \Fig{CO21mom}, and
the higher-order first and second moment maps in \Fig{CO21highO}
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The renzogram is created using different velocity channels for the blue- and
redshifted velocity components and
the higher-order moment maps are created using
channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity-integrated map.

The deconvolved source size FWHM
is estimated to be 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, we therefore take this as an estimate on the extent of the lensed
emission. On the other hand, if we assume the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \nir
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein Ring'' and
the lensed knots (see \Fig{CO21mom}).

\begin{figure}[!htbp]
\includegraphics[trim=0 10 15 0, clip, width=0.222\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=5 -10 0 0, clip, width=0.232\textwidth]{../Figures/F555W_REDBLUE.eps}
\caption{Left: an overlay of the velocity-integrated \bco emission on the {\it HST} $V$--band (F555W)
image. Right: contours are color-coded to represent the red and blue wings of the emission.
The contours start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne. The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
\label{fig:CO21mom}}
\end{figure}

\begin{figure}[!htbp]
%\centering
\includegraphics[width=0.45\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\caption{
Contours for the first (left) and second (right) moment maps are shown in steps of
50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
\label{fig:CO21highO}}
\end{figure}

We also place an upper limit on \rot[HNC]{2}{1} line emission
in the foreground galaxy at $z\sim$0.295.
Assuming a typical line width of 300\,\kms, this corresponds to a 3$\sigma$
limit of 0.35\,mJy\,\kms\,beam\pmOne.

\subsection{\cco Emission}
We detect \cco line emission toward RXJ1131 at {\bf BLAH}$\sigma$ significance.
The spectrum is shown in \Fig{co32spec}, which seems to have a double-peak profile.
This is expected if RXJ1131 is truly a disk galaxy (see previous
sections). The high phase noise in the calibration leads to a low SNR
detection. We thus estimate the line intensity to be
35.7\,$\pm$\,21.9{\bf BLAH} Jy\,\kms by summing up fluxes over the FWZI
linewidth used to infer \bco line intensity ($\sim$700 \kms).

\begin{figure}[!Htbp]
%\centering
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is with respect to $z$=0.6537, which corresponds to the
dynamical center of the \bco line. The spectral resolution for \cco and \bco
is 35.8 \kms and 21.5 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

Assuming the spatial extents between \bco and \cco are similar and therefore
magnified by the same amount, the line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,T$_{\small \cco}$$/$T$_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.

>>>>

\title{Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131-1231 at $z$=0.654}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

%=============================================================================
%                                Front matters
%==============================================================================

\begin{abstract}
We report interferometric observations of \bco and \cco emission toward the gravitationally lensed 
quasar RXS J1131-1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
This is the first resolved \bco imaging at intermediate redshift.
RXS J1131-1231 ?. 
evidence for differential lensing.
wet-merger, Dynamical lens modeling
the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
is indicative of, and suggests...
% Our results is consistent with the picture that gas-rich mergers may evolve into small bulge disk galaxies.
% MBH-sigma relation...
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
Despite the recent progress in theoretical models and observational studies...on understanding the evolution of massive galaxies.
% interplay between / role of Complex baryonic physics such as mergers, gas dissipation, and feedback..
It is not known when and how the main baryonic components of modern galaxies formed/assembled, but the global 
stellar mass density rose substantially between z\ssim1$-$3, reaching $\sim$50\% of its present value by z\ssim1 
(\ie how high-z galaxies evolve into present-day galaxies.)
As such, studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 is important to unravel/understand the cause for the rapid decline in star formation and BH accretion rates (e.g. Madau et al. 1998, Hopkins \& Beacom 2006). 
Studies of galaxy evolution find SFRD and BHAH peak at
$z$\ssim2 and declines rapidly toward $z$$=$0. A leading explanation for such
a trend is the evolution of molecular gas content and SFE in galaxies (CW13).
While we know blah at the local universe and studies of the gas properties at
high-z are also emerging in recent years (see CW13 for a review). It is still
unclear what mechanism is responsible for removing cold gas from galaxies and
shutting down their star formation to build-up present-day red sequence
galaxies, leading to a change of slope at high \mstar (esp. at $z$ $<$ 1.5),  i.e.
suppression of SFR at high \mstar, i.e. strong evolution in sSFR (of massive gal.)
(cite: Papovich, Whitaker+12, Magnelli+14, Schreiber+15, Lee+15).
It has been proposed that the high SFR at high-$z$ is due to the higher gas fraction than local (Erb et al. 2006), 
regardless of their position in the SFR$-$M$^*$ plane, both MS and SB at high z have depletion time that is much 
short than local, suggesting more efficient mode for SF. 
Up to now, very little is known about the molecular gas content at moderate z. The ULIRG sample of Solomon97 contains 37 objects, but only 2 at are z $>$ 0.2. With the advance in mm-instruments, Combes11a investigate the variation of molecular gas and SFE in an expanded sample of 30 ULIRGs with CO observations.

%why AGN host 
In the current paradigm, SMBHs grew in every massive galaxy during a luminous quasar phase, 
where distant QSOs are the progenitors of the passive SMBHs in nearby galaxies.
Locally, the connection between AGNs and their host galaxies is described 
through the well-established tight correlation between BH mass 
and stellar velocity dispersion (CITE), implying growth of the SMBH and their host galaxies is co-eval.
However, it is unclear if this relation holds/or how the co-evolution BLAH at high-$z$.
Recently, theoretical and observational studies of the co-evolution of SMBHs and their host galaxies
have been attempting to extend this relation out to higher-$z$, beyond the peak epoch 
of \SF and AGN activity (CITE).

% difference proxy to the relation
Since it is not trivial to obtain measurement of stellar dispersion (rely on spatially resolved stellar kinematics) at high-$z$, 
efforts in calibrating and understanding how 
the use of dynamical mass or stellar bulge mass \citep[\eg][]{Peng06a} or 
stellar luminosity as a proxy for stellar dispersion.
At high-$z$, more CO measurements have been obtained at high-z, and
one can obtain dynamical mass through CO linewidth and spatial extent.

Based on the \mbh$-$\mdyn relation, there are considerable evidence now that high-z BHs grow faster than their host galaxies.
The dynamical mass inferred from CO velocity structure (line width) and spatial extent is lower than that 
based on local relation. 
Current results imply high-$z$ galaxies ($z$$>$BLAH) do not follow this relation, where their observed $M_\textrm{dyn}$ is lower than that inferred from
this relation or \mbh$/$$M_{*}$ is smaller high-$z$ than today \citep{Borys05a}. 
This implies that a quasar phase is needed in order for high-z galaxies to evolve 
onto the local \mbh$-$$M_{\rm bulge}$ relation / high-$z$ BH grow faster than their host galaxies, 
as predicted in simulations where feedback is needed in order to explain the 
anti-hierarchical growth of galaxies / suppress efficient early star formation
and the lack of more massive galaxies as would be produced without feedback. 
But how investigate this evolution at intermediate redshift is challenging,
because it also suffers the same cosmological dimming issue at high-$z$ studies, time-consuming to obtain
resolved CO observations for intermediate-z.

One way to understand is to investigate the relation as different epochs more closely.
We still lack a clear picture of relationship between AGN and hosts since we do not know much at the intermediate redshifts where both \SF and AGN accretion slow down.
It appears that there may be a decreasing trend from $z$$>$3 to 1$<$3 and compared to the local fit.
But it is clear that there is a desert in between these redshift range.

Host galaxies of AGN are difficult to study because the quasar usually dominates the observed light, and ?.
With gravitational lensing, the stellar emission and quasar emission in RXJ1131 
are magnified and stretched out at different locations to different extents in the image plane, gaining 
the surface brightness contrast to enable measurements of their emission separately.
RXJ1131 thus provide a unique laboratory to study the ?

%--------
In this paper, we explore the well-established local BLAH relations to intermediate redshift
and investigate the postulated decrease gas fraction from BLAH studies at intermediate 
redshift.
We use BLAH to study the ISM properties of the quadruply imaged
quasar RXS J113151.62-123158 (hereafter RXJ1131) at
$z_\textrm{s, QSO}$\eq0.685, lensed by an
elliptical galaxy at $z_\textrm{L}$\eq0.295. The redshifts 
are spectroscopically confirmed by \citet[hereafter S03]{Sluse03a}.
Emission in the host galaxy of RXJ1131 is lensed into an Einstein ring of size 1\farcs83 in radius.
The black hole of mass \mbh\,$<$\,2\E{8}\Msun\footnote{Various values for the black hole 
mass have been reported based on the different methods and normalizations used. \citet{Dai10a} find a 
\mbh\ssim10$^{8}$\,\Msun using the virial estimator with H$\beta$ linewidth,
and \citet{Pooley07a} report $M_{\rm BH}$\,=\,2.5\E{7}\,\Msun using the
AGN bolometric luminosity of $L_{\rm bol, X}$ =1.3\E{45}\, ergs\,s\pmOne, 
assuming $L$$/$$L_\textrm{Edd}$ = 0.25 and $\eta$ = 0.15.}
residing in RXJ1131 has been observed to 
be rotating with a high spin parameter
\citep[$a$\,$\sim$\,0.9;][]{Reis14a}.
\defcitealias{Sluse03a}{S03}

This paper is structured as follows.
In \Sec{obs} and \Sec{HST}, we outline the details of the observations and data reduction process.
In \Sec{results}, we report the measurements of the CO lines and photometry from optical to radio wavelengths.
In \Sec{anal}, we present dynamical lens modeling of the \bco data and the physical properties inferred for  RXJ1131.
In \Sec{diss}, we discuss the results and implications of this study in the context of molecular gas in mergers and ULIRGs {\bf BLAH}.
Finally, we summarize the main results of this study and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = 69.32 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.29, and
$\Omega_{\Lambda}$ = 0.71 \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,230.5379938 GHz) redshifted to $\nu_{\rm obs}$\,=\,139.0\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively. The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup providing
an effective bandwidth of 3.6 GHz (dual polarization) and a spectral resolution of 10.0 MHz ($\sim$
21.5 \kms). This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding $\lesssim$15\% calibration accuracy.

The \ncode{gildas} package was used to reduce and analyze the visibility data.
The calibrated visibility data were imaged and deconvolved using the CLEAN algorithm with ``natural''
weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
The final rms noise is $\sigma$\,=\,1.45\,mJy\,beam\pmOne
over 10 MHz (21.5\,\kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
is created by averaging over 3.16\,GHz of line-free bandwidth. This
yields an rms noise of 0.082 mJy\,beam$^{-1}$. % see README.md in 04Sep15

\subsection{CARMA \cco}
Observations of the \cco rotational line in RXJ1131
($\nu_{\rm rest}$\,=\,345.7959899\,GHz) redshifted to $\nu_{\rm obs}$\,=\,208.6\,GHz
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions. The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks. This results in a total on-source time of 2.94 hours after flagging poor
visibility data.

% poor phase note
% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
% rms scatter over ~ 90 klambda
% max baseline of obs. is 145 m
%
% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710
%
Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$60$\degr$ over a baseline length of $\sim$135\,m.
%BLAH... more like 50%
We thus conservatively estimate
a calibration accuracy of $\sim$45\% based on the flux scale uncertainties,
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat its line intensity with caution and ensure that our physical interpretation
of this system does not rely on this quantity.

The \ncode{miriad} package was used to calibrate the visibility data.
The calibrated visibility data were
imaged and deconvolved using the CLEAN algorithm with ``natural'' weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA\,=\,8\degr) for the lower sideband
image cube. The final rms noise is $\sigma$ = 13.3 mJy beam$^{-1}$
over a channel width of 25\,MHz. An rms noise of
$\sigma$\,=\,0.83\,mJy\,beam\pmOne is reached by averaging over the
line-free channels.

\subsection{VLA (Archival)} %DONE
Our analysis also uses archival data of the 5\,GHz
radio continuum obtained with the
Very Large Array (VLA; Program ID: AW741; PI: Wucknitz).
Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configuration for a total of $\sim$7 hours on-source time. The C-band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz for the two IF bands with full polarization.
The nearby radio quasar J1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration, J1331$+$305 was observed as the
primary flux calibrator, and J0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We used \ncode{aips} to calibrate the visibility data.
The calibrated visibility data were imaged and deconvolved using
the CLEAN algorithm using robust\,=\,0. This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0.18$\degr$) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

\section{HST astrometry} \label{sec:HST}
We obtained an {\it HST} image taken with
the ACS/Wide Field Camera 
using the F555W filter ($V$-band)
from the
Hubble Legacy Archive\footnote{Based on observations
made with the NASA/ESA Hubble Space Telescope, and obtained from the Hubble
Legacy Archive, which is a collaboration between the Space Telescope Science
Institute (STScI/NASA), the Space Telescope European Coordinating Facility
(ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).}. 
The details of the observations can be found
in \citet[hereafter C06]{Claeskens06a}.
We adopt the VLA 5\,GHz map as the
reference coordinate frame to align the optical ($V$-band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$^{\prime\prime}-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. This astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is guided by its
coordinates in the optical image, where its emission is clearly detected.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have an astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR and phase
instability.
\defcitealias{Claeskens06a}{C06}

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\subsection{\bco Emission} \label{sec:CO21} %DONE
We detect \bco line emission toward the background source
at $\gtrsim$27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
0.65370\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
is with respect to $z$\,=\,0.6537, which is approximately the line center
considering the asymmetry as a result of differential lensing.
A detailed discussion of this effect is presented in
\Sec{differential} and the magnification factors for various kinematic
components are listed in \Tab{model}.
 \label{fig:CO21spec}}
\end{figure}

% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct the zeroth moment map, a red/blue channel map, and
the first and second moment maps in \Fig{CO21mom}
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are created using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity-integrated map.

The deconvolved source size FWHM from two-dimensional Gaussian fitting
is estimated to be 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, we therefore take this as an estimate on the extent of the lensed
emission. On the other hand, if we assume the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \nir
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein ring'' and
the lensed knots (see \Fig{CO21mom}).

\begin{figure*}[!htbp]
\hspace{0.5em}
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=5 -10 0 0, clip, width=0.472\textwidth]{../Figures/F555W_REDBLUE.eps} 
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on the archival {\it HST} $V$-band (F555W)
image. 
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission.
The contours in both top panels start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel, 
and 
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively. 
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

We also place an upper limit on \rot[HNC]{2}{1} line emission
in the foreground galaxy at $z\sim$0.295.
Assuming a typical line width of 300\,\kms, this corresponds to a 3$\sigma$
limit of 0.35\,Jy\,\kms\,beam\pmOne.

\subsection{\cco Emission}
We detect \cco line emission toward RXJ1131 at {\bf BLAH}$\sigma$ significance.
The spectrum is shown in \Fig{co32spec}, which appears to be consistent with a 
double-peaked profile. We estimate a line intensity of
35.7\,$\pm$\,21.9{\bf BLAH} Jy\,\kms by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).
Assuming the spatial extent between \bco and \cco are similar and therefore
magnified by the same amount, the line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
